Contention Management for 5G

### 2017-05-30 article/article.tex
openmp + article suite

\maketitle
\begin{abstract}
We study the sending of periodic messages in a graph following predefined paths, a problem arising from the communication between radio antenna and their computing unit located in distant data-centers.  We want to send the messages so that there are no congestion while minimizing the latency. We prove the problem is $\NP$-complete even when the graph is very simple. We then deal with the case of a star graph and for different regime of the parameters we propose several algorithms that are experimentally shown to work extremely well.
\end{abstract}

@@

	The different sending policy that we tried are the following :
	\begin{enumerate}
	 \item Random: Generate $X$ random permutations for the routes and tries the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic affectation.
	 \item Longest-Shortest on Routes (LSR): Send the messages from the one using longest to the one using shortest route (this is the sending order used in the previous heuristic).
	 \item Shortest-Longest on Routes (SLR): Send the messages from the one using shortest to the one using longest route
	 \item Longest-Shortest on last Arc (LSA): Send the messages from the one having the longest arc between $c_t$ an the target to the one having the shortest one.
	 \item Shortest-Longest on last Arc (SLA): Send the messages from the one having the shortest arc between $c_t$ an the target to the one having the longest one. This sending order gives us some $(P,\tau)$ periodic affectation in which all the $w_i = 0$, but needs a huge period if the difference between the longest and the shortest route is large (see proposition \ref{prop:SL}).
	\end{enumerate}

@@

   We look at two different regimes: one in which the period represents $1,05n\tau$, and one with a greater period $1,5n\tau$. The following results are computed over 10000 instances.

>>>>

\maketitle

\begin{abstract}
We study the sending of periodic messages in a graph following predefined paths, a problem arising from the communication between radio antenna and their computing unit located in distant data-centers.  We want to send the messages so that there are no congestion while minimizing the latency. We prove the problem is $\NP$-complete even when the graph is very simple. We then deal with the case of a star graph and for different regime of the parameters we propose several algorithms that are experimentally shown to work extremely well.
\end{abstract}

@@

	The different sending policy that we tried are the following :
	\begin{enumerate}
	 \item Random: Generate $X$ random permutations for the routes and tries the greedy heuristic on the way back until we get an available $(P,\tau)$ periodic affectation. In the following experiments, we take $X = 100$.
	 \item Longest-Shortest on Routes (LSR): Send the messages from the one using longest to the one using shortest route (this is the sending order used in the previous heuristic).
	 \item Shortest-Longest on Routes (SLR): Send the messages from the one using shortest to the one using longest route
	 \item Longest-Shortest on last Arc (LSA): Send the messages from the one having the longest arc between $c_t$ an the target to the one having the shortest one.
	 \item Shortest-Longest on last Arc (SLA): Send the messages from the one having the shortest arc between $c_t$ an the target to the one having the longest one. This sending order gives us some $(P,\tau)$ periodic affectation in which all the $w_i = 0$, but needs a huge period if the difference between the longest and the shortest route is large (see proposition \ref{prop:SL}).
	\end{enumerate}

@@

   We look at two different regimes: first, we take a period equal to $1,05n\tau$, and then, we take a greater period, that is, $1,5n\tau$. The following results are computed over 10000 instances.
